Efficient Coalition Formation \\ for Web Services

### 2013-05-31 papers/coalition-journal-extension/coalition_journal.tex
Changes

\subsection{Web Service Parameters}

@@

The community master uses a slightly modified \emph{weighted fair queuing} method to distribute task among its members. The goal is to allocate incoming tasks to web services with a rate matching throughput value of $Tr_{ws}$. In \emph{weighted fair queuing} method \emph{all} the input flow is multiplexed along different paths, however in our case if the input rate $(R_C)$ of the community is more than summation of throughput values of web services, some of the input tasks will be queued and served with delay. Thus, the amount of tasks performed by community is $\sum_{ws \in C}{(Tr_{ws})}$ when $\sum_{ws}{Tr_{ws}} \leq R_{C}$. However, when the community has more web services having more total throughput value than community's request rate $(R_C)$ the \emph{weighted fair queuing} algorithm assigns a weighted task rate of $R_C \times \frac{Tr_{ws}}{\sum_{ws}{Tr_{ws}}}$ for each web service ($ws$) and the total rate of tasks being performed is $R_C$, the community's receiving request rate. The best situation for communities would be to have around the same number

\section{Web Service Cooperative Games}\label{s:model}

>>>>

\subsection{Web Service Parameters}\label{ws_parameters}

@@

The community master uses a slightly modified \emph{weighted fair queuing} method to distribute task among its members. The goal is to allocate incoming tasks to web services with a rate matching throughput value of $Tr_{ws}$. In \emph{weighted fair queuing} method \emph{all} the input flow is multiplexed along different paths, however in our case if the input rate $(R_C)$ of the community is more than summation of throughput values of web services, some of the input tasks will be queued and served with delay. Thus, the amount of tasks performed by community is $\sum_{ws \in C}{(Tr_{ws})}$ when $\sum_{ws}{Tr_{ws}} \leq R_{C}$. However, when the community has more web services having more total throughput value than community's request rate $(R_C)$ the \emph{weighted fair queuing} algorithm assigns a weighted task rate of $R_C \times \frac{Tr_{ws}}{\sum_{ws}{Tr_{ws}}}$ for each web service ($ws$) and the total rate of tasks being performed is $R_C$, the community's receiving request rate.

\subsection{Community Revenue}

The communities and web services earn revenue by performing tasks. The total gain is function of quality ($QoS_{ws}$) and quantity($Tr_{ws}$) of tasks being performed. As mentioned in section \ref{ws_parameters} $QoS_{ws}$ is obtained by a certain aggregation function of the parameters considered in Table \ref{qosws}. We have adopted a linear equal weigth average over all QoS parameteres listed in table \ref{qosws} excluding the $Throuput$ and $Cost$ parameters. A community has the option to weigh specific QoS patameters more or less depending on the expectations of their clients.

The maximum potential output $(PO(C))$ of a community is aggregation of number of tasks, times their quality, for each web service participating as a member of the community:

\begin{equation}
PO(C) = \sum_{ws \in C}{(T_{ws} \times QoS_{ws})}
\end{equation}

If the summation of throughput ($Tr_{ws}$) values of community members exceeds the input task rate of the community ($R_C$) the community cannot perform at its maximum potential. It means community has more web services than it needs for performing input task load. Therefore, in these cases, the actual output has to be normalized to the ammount of tasks being performed.

\begin{equation}
Out(C) = \left\{
  \begin{array}{l l}
    PO(C) & \quad \text{if $\sum_{ws}{Th_{ws}} \leq R_{M}$}\\
    PO(C) \times \frac{R_{M}}{\sum_{ws}{Th_{ws}}} & \quad \text{if $\sum_{ws}{Th_{ws}} > R_{M}$}
  \end{array} \right.
\end{equation}

The revenue function of the web service community, is a linear function of $Out(C)$ with a positive constant multiplier.

\subsection{Case Study}

In this section, we analyse a few numerical examples and discuss the motivation of web services and community intractions and the strategies they can adopt and the revenue they can earn adopting different strategies.

%%%%%%%%%%%%%%%%%%%%%%%%% EXAMPLE 1 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[!t]
\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
\caption{Three web services of example 1}
\label{example_1}
\centering
\begin{tabular}{c c c c}
\hline
$WS$ & $QoS_{ws}$ & $Th_{ws}$ & $Th_{ws} \times QoS_{ws}$\\
\hline
1 & 0.8 & 4 & 3.2\\
1 & 0.8 & 5 & 4.0\\
1 & 0.8 & 3 & 2.4\\
\hline
\end{tabular}
\end{table}

\begin{table}[!t]
\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
% \caption{Three web services}
\label{example_1_1}
\centering
\begin{tabular}{c c || c c}
\hline
Community & Value & Community & Value\\
\hline
$\left\{1\right\}$ & 3.2 & $\left\{1,2\right\}$ & 7.2\\
$\left\{2\right\}$ & 4.0 & $\left\{1,3\right\}$ & 6.8\\
$\left\{3\right\}$ & 2.4 & $\left\{2,3\right\}$ & 6.4\\
$\left\{1,2,3\right\}$ & 8.0\\
\hline
Community $R_C$: 12\\
\hline
\end{tabular}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%% EXAMPLE 1 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%% EXAMPLE 2 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[!t]
\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
\caption{Three web services of example 2}
\label{example_2}
\centering
\begin{tabular}{c c c c}
\hline
$WS$ & $QoS_{ws}$ & $Th_{ws}$ & $Th_{ws} \times QoS_{ws}$\\
\hline
1 & 0.8 & 5 & 4.0\\
1 & 0.7 & 6 & 4.2\\
1 & 0.7 & 4 & 2.8\\
\hline
\end{tabular}
\end{table}

\begin{table}[!t]
\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
% \caption{Three web services}
\label{example_2_2}
\centering
\begin{tabular}{c c || c c}
\hline
Community & Value & Community & Value\\
\hline
$\left\{1\right\}$ & 4.0 & $\left\{1,2\right\}$ & 7.4\\
$\left\{2\right\}$ & 4.2 & $\left\{1,3\right\}$ & 6.8\\
$\left\{3\right\}$ & 2.8 & $\left\{2,3\right\}$ & 7.0\\
$\left\{1,2,3\right\}$ & 7.3\\
\hline
Community $R_C$: 10\\
\hline
\end{tabular}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%% EXAMPLE 2 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

In the first example, we present a community with $R_C$ of 10, and three web services each having different $QoS$ and $Th_{ws}$ values as listed in table \ref{example_1}.

\section{Web Service Cooperative Games}\label{s:game_solution}
